Analysis-ready VCF at Biobank-scale using Zarr

### 2024-05-08 paper.tex

\begin{figure}
\includegraphics{figures/column-extract}
\caption{Time to extract the genome position and write to a text file.
Total CPU time required to extract the POS field for BCF,
sav and Zarr formats
for the data in Figure~\ref{fig-data-storage}.
For the BCF file we used \texttt{bcftools query -f"\%POS$\backslash$n"}.
For sav, we used the Savvy C++ API to extract just the position, 
and output text using the \texttt{std::cout} stream. For Zarr, we read 
\texttt{variant\_position} into a NumPy array, and then wrote to
a text file using the Pandas
\texttt{write\_csv} method. Writing
text dominates in the case of Zarr: populating the NumPy array 
in memory takes less than a second in all cases. Genozip does
not offer an option to extract individual columns, and so would require
the output to be piped into \texttt{bcftools query} or a
Unix utility such as \texttt{cut}.
\label{fig-column-extract}}
\end{figure}

>>>>

\begin{figure}
\includegraphics{figures/column-extract}
\caption{Time to extract the genome position and write to a text file.
Total CPU time required to extract the POS field for BCF,
sav and Zarr formats
for the data in Figure~\ref{fig-data-storage}.
For the BCF file we used \texttt{bcftools query -f"\%POS$\backslash$n"}.
For sav, we used the Savvy C++ API to extract just the position, 
and output text using the \texttt{std::cout} stream. For Zarr, we read 
\texttt{variant\_position} into a NumPy array, and then wrote to
a text file using the Pandas \texttt{write\_csv} method. 
Zarr CPU time is dominated by writing the text output; we also show
the time required to populate a NumPy array with the data in Zarr,
which is less than a second. Wall-clock time (dotted line) is dominated 
in this case by file I/O. Time to output text for Savvy is not significant
for $> 1000$ samples (not shown).
\label{fig-column-extract}}
\end{figure}
